Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-07 WSSSPE2_report/WSSSPE2_review.tex
Section 4: raw summary from speaker.

%\item Samin Ishtiaq: Daemons, Notifications and Sustaining Software

>>>>

\item Samin Ishtiaq: Daemons, Notifications and Sustaining Software
%  Microsoft Research Cambridge

The reproduction and replication of novel results has become a major issue in
computer science, systems biology and other computational disciplines. These
include both the inability to re-implement novel algorithms and approaches, and
also an agreement on how and what to benchmark these algorithms on.

In the talk, we discussed these problems and suggested several suggestions to
address them.
